Through the eyes of the teacher - Multimodal exploration of expertise differences in the perception of classroom disruptions in a laboratory study

### 2024-11-07 02_paper/02_study/02_expertise_paper/expertise_2024_09_26_no_outlierdetection_MK.Rmd

>>>>

#### 2.2.2 Number of fixations per minute (AOI others)
```{r nof_others, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

##################### NUMBER OF FIXATIONS (AOI others) ########################

# filter group & total duration & number fixation (AOI others)
df_aoi %>%
  filter(TOI == "Lesson") %>%
  dplyr::select (
    Group,
    Duration_of_interval,
    Participant,
    "Total_duration_of_fixations.Board_Screen",
    "Total_duration_of_fixations.Classroom_Others",
    "Total_duration_of_fixations.Material_Students",
    "Total_duration_of_fixations.Material_Teacher",
    "Total_duration_of_fixations.Nametag_Anna",
    "Total_duration_of_fixations.Nametag_Bianca",
    "Total_duration_of_fixations.Nametag_Carl(a)",
    "Number_of_fixations.Board_Screen",
    "Number_of_fixations.Classroom_Others",
    "Number_of_fixations.Material_Students",
    "Number_of_fixations.Material_Teacher",
    "Number_of_fixations.Nametag_Anna",
    "Number_of_fixations.Nametag_Bianca",
    "Number_of_fixations.Nametag_Carl(a)"
  ) %>%
  rowwise() %>%
  transmute(
    Group = as_factor(Group),
    Duration_of_interval_min = round(Duration_of_interval/60000, digits = 2),
    Duration_of_interval_sec = round(Duration_of_interval/1000, digits = 2),
    Participant = Participant,
    Others_duration_fixation = sum(c_across(starts_with("Total_duration")), na.rm = TRUE),
    Others_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE),
    Others_number_fixation_min = round(Others_number_fixation / Duration_of_interval_min, digits = 2),
    Average_duration_others = round(Others_duration_fixation / Others_number_fixation, digits = 0)
    ) -> df_aoi_others

# N, M, SD, min & max number of fixations per minute (AOI students)
nof.min.others.table <-
  df_aoi_others %>%
  group_by(Group) %>%
  summarise(
    N = n(),
    "M" = round(mean(Others_number_fixation_min), digits = 2),
    "SD" = round(sd(Others_number_fixation_min), digits = 2),
    "Min" = round(min(Others_number_fixation_min), digits = 2),
    "Max" = round(max(Others_number_fixation_min), digits = 2)
  )

knitr::kable(nof.min.others.table,
             caption = "N, M, SD, min & max number of fixations per minute (AOI others)")

#### t-test & effect size "Number of fixation" (AOI others)
```{r nof_others_ttest, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

# NUMBER OF FIXATIONS on AOI others 
# t-test for expertise differences
t.test(
  x = df_aoi_others$Others_number_fixation_min[df_aoi_others$Group == "Expert"],
  y = df_aoi_others$Others_number_fixation_min[df_aoi_others$Group == "Novice"],
  var.equal = TRUE
)

# NUMBER OF FIXATIONS on AOI students
# effect size for expertise differences
d_number_others <- CohenD(
  x = df_aoi_others$Others_number_fixation_min[df_aoi_others$Group == "Expert"],
  y = df_aoi_others$Others_number_fixation_min[df_aoi_others$Group == "Novice"],
  na.rm = TRUE
)

round(d_number_others, 2)
